Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-16 prop_iop.tex
prop.bib @Article{Bell1964} Updated, and update the font encoding...
prop_iop.tex \section{Why Empty Core?} Starting...

\documentclass[12pt]{iopart}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}

@@

In informal terms, this result states that although measurements done
with limited resources and poor precision may not uniquely identify
the true state of the system, there is always at least one system that
is consistent with the measurements. Surprisingly, we discovered a
counterexample to this statement in the quantum case, i.e., we
constructed the following convex quantum interval-valued probability
measure with an empty core.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.38]{figure2.eps}
\end{center}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates
  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
  and $\ket{\ps}$ respectively.  All possible real vectors of the subspaces
  $\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
  circles, respectively. Within the circles, a dotted
  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
  green solid vectors are normalized
  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively, where
  $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
\end{figure}

Looking closely at the example above, we might think that the probability
measure $\bar{\mu}$ is induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or we might think it is induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
or yet we might think it is induced by the mixed state $\mathbb{1} / 3$
because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$.
Each of these possibilities is compatible with some but not all of
the observations. All is not lost however: if the observations are
made more precise, we conjecture that some of the inconsistencies
disappear. A partial proof of this conjecture is the following example
which refines the previous convex probability measure by adding more
precise intervals.

>>>>

\documentclass[12pt]{iopart}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}

@@

In informal terms, this result states that although measurements done
with limited resources and poor precision may not uniquely identify
the true state of the system, there is always at least one system
that is consistent with the measurements. Surprisingly, we discovered
a counterexample to this statement in the quantum case, and have the
following theorem.

\begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
There is a convex quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.\end{thm}

This theorem could be proved by constructing the following convex
quantum interval-valued probability measure with an empty core.

@@

\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figure2} 
\par\end{centering}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates cases
1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted in
$\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
and $\ket{\ps}$ respectively. All possible real vectors of the subspaces
$\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}$
are drawn in the red and green circles, respectively. Within the circles,
a dotted vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is
a generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red
and green solid vectors are normalized $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$
and $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively,
where $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
\end{figure}

\section{Why Empty Core?}

Notice that in the previous section,

\subsection{Convexity}

\subsection{From Quantum to Classical}

\subsection{Increase the Measurement Resource}

Looking closely at the example above, we might think that the probability
measure $\bar{\mu}$ is induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or we might think it is induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
or yet we might think it is induced by the mixed state $\mathbb{1}/3$
because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$.
Each of these possibilities is compatible with some but not all of
the observations. All is not lost however: if the observations are
made more precise, we conjecture that some of the inconsistencies
disappear. A partial proof of this conjecture is the following example
which refines the previous convex probability measure by adding more
precise intervals.
